\documentclass[11pt,twoside,a4paper]{article}
\author{Catherine Vlasov}
\title{3rd Year Project Report}
\begin{document}
\maketitle
\section{What I Learned}
This has been a really great learning experience, not only in terms of discovering the field of reinforcement learning and its applications, but also in terms of gaining experience with building up a large, complex programming project from scratch using a variety of technical tools.

When I was in high school, I designed and implemented the classic board game Nine Men’s Morris where a user plays against an algorithm I wrote. My plan for the project was to ask my friends and family to play my game and to store the moves made in each game so that I could build up a database of sequences of moves and outcomes of the game. I hoped to somehow compute which moves were the best and get my algorithm to learn which moves made winning the most likely. Little did I know, I wanted to invent RL from scratch – unaware of its existence or of the amount of research in the field. Several years later, I am delighted to have had the chance to work on a similar project, but this time on a deeper level using well-known computational algorithms.

When I started working on this project, I decided to treat it as an opportunity to develop many skills that are critical for a career in software engineering:
\begin{itemize}
\item[-] Writing clean, maintainable, well-documented code
\item[-]Designing and implementing tests for my code
\item[-]Using a build tool to manage dependencies between packages in my project as well as with external libraries
\item[-]Using version control effectively
\end{itemize}
I tested the methods in my API using a unit-testing framework for Java called JUnit. I also used a testing framework for Java called Mockito – this allowed me to verify the behaviour of objects with external dependencies by creating “mock objects” for theses dependencies, which mimic real objects but do so in a particular way that I can specify.

In order to save my experiment results in a format that would facilitate the creation of graphs, I used opencsv, a CSV parser library for Java.

To manage my project’s dependencies, I used a build tool developed by Google called Bazel and I used Git for version control.

Overall, I really enjoyed learning about RL algorithms and exploring their applications and success rates, all while developing strong programming skills that will help me throughout my career.
\end{document}